%-------------------------
% Resume in Latex
% Author : Venugopal Pai
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Ajay Ragh}} & Email : \href{mailto:ajayragh345@gmail.com}{ajayragh345@gmail.com}\\
  \href{ }{ } & Mobile : +91-8086854636 \\
  \href{ }{ } & \href{https://github.com/ajayragh97/ }{github.com/ajayragh97}
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Graduate in electronics and communication engineering with experience in the fields of data analysis,algorithm simulation and transparent electronics.
\begin{itemize}
  \item Analyzing,inferring and optimizing governmental models as part of data science project. 
  \item Prototyping,testing and validating of algorithms in  swarm robotics. 
  \item Socially committed and an active participant in building a technologically aware and active community of youngsters, thereby empowering them to solve the vital challenges of society through technology and alternative education. 
\end{itemize}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Government Engineering College}{Barton Hill, Thiruvananthapuram, India}
      {Bachelor of Technology in Electronics and Communication;  GPA: 7.23}{July. 2015 -- June. 2019}
    \resumeSubheading
      {Kerala State open school}{Calicut,India}
      {Percentage: 91}{June. 2013 -- May 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------


\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Augsense Lab}{Thiruvanathapuram, India}
      {Research Engineer}{December 2019 - Present}
      \resumeItemListStart
        \resumeItem{Computer Vision based NWP}
          {Predicting extreme weather patterns for Numerical Weather Prediction(NWP) using deep learning algorithms and opencv from radar images }
          \begin{itemize}
              \item Identifying and collection of data from radar images .
              \item Creating deep learning models using Tnsor flow and Keras .
              \item Optimising deep learning model for increased accuracy.
         \end{itemize}
         
        \resumeItem{SLAM}
          {Improving Simultaneous Localisation And Mapping (SLAM) algorithm ORBSLAM for increased performance in multiple environments. }
          \begin{itemize}
              \item Identifying and collection of data from datasets .
              \item Creating optimization algorithms for improving the quality of data to be fed into the SLAM algorithm  .
         \end{itemize}
         
      \resumeItemListEnd
      
    \resumeSubheading
      {FOSSEE-IIT Bombay}{Thiruvanathapuram, India}
      {Fellowship}{March 2019 - July 2019}
      \resumeItemListStart
        \resumeItem{RECYCLE}
          {Statistical analysis of current waste management model in Thiruvananthapuram district of Kerala,India and successful development of an optimized decentralized waste disposal model. }
          \begin{itemize}
              \item Identifying and collection of key data points.
              \item Statistical analysis of collected data.
              \item Developed mathematical model based on the results inferred from the statistical analysis.
         \end{itemize}
      \resumeItemListEnd

    \resumeSubheading
      {Infinity Labs}{Technopark, Thiruvanathapuram, India}
      {Internship}{Sept 2017 - Dec 2017}
      \resumeItemListStart
        \resumeItem{Research Intern}
          {Conduct research and prototype products in the fields of nanomaterials and autonomous vehcles. }
      \resumeItemListEnd
      
      \resumeSubheading
      {All India Radio}{Thiruvanathapuram, India}
      {In-Plant trainee}{July 2016}
      \resumeItemListStart
        \resumeItem{In-Plant trainee}
          {1 week training at the different facilities and studios of AIR Thiruvananthapuram where we were made familiar with the different devices and techniques they used at their facilities.}
      \resumeItemListEnd


\section{Volunteer Experience}
      \resumeSubheading
      {Sahridhaya}{Statue, Thiruvanathapuram, India}
      {Developer}{Dec 2018 - Present}
      \resumeItemListStart
      \resumeItem{Sahridhaya} {aims to bring the youth a fresh opportunity to participate in social events and establish the need for social responsibility and social commitment.}
        \resumeItem{Bit Please}
          {A group of college students initially formed to learn programming and problem solving skills.The latest achievement of our team was working with the district collectors office on optimization problems on waste management model followed in  the city.}

      \resumeItemListEnd
      

% %-----------PROJECTS-----------------
% \section{Projects}
 %  \resumeSubHeadingListStart
  %   \resumeSubItem{Recycle}
%       {Statistical analysis project on waste management model being followed in Thiruvananthapuram,India.}
 %    \resumeSubItem{Hybrid Swarm Optimization }
  %     {Research Projecton creating a hybrid algorithm based on swarm optimization algorithms }
   %  \resumeSubItem{Free India-file registry system}
    %   {OT based file registry system that provides applicants access to the current status of their application filed at government offices.
%}
 %  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
% \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: R,MATLAB,Python,C++}
%   }
% \resumeSubHeadingListEnd


%-------------------------------------------
\end{itemize}
\end{document}
