%-------------------------
% Resume in Latex
% Author : Venugopal Pai
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Venugopal Pai}} & Email : \href{mailto:venugopalgpai@gmail.com}{venugopalgpai@gmail.com}\\
  \href{ }{ } & Mobile : +91-9633813585 \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Graduate in Electronics and Communication with expertise in development, prototyping, analysis, and implementation of algorithms in Image Recognition, Object detection, 3D Reconstruction and fluoroscopic sequential data processing.
\begin{itemize}
  \item Proficient in software engineering concepts, principles, and techniques with a proven competitive and professional track record.
  \item Reputation for defining, testing, and validating complex architectures for high scalability and high-performance environments.
  \item Adept at working with large and complex data sets to develop methodologies to foster the creation of novel software applications.
  \item Ability to adapt rapidly to new environments and fields of study, such as mathematical modeling, machine learning and its applications across fields like bio-medical and finance.
  \item Socially committed and an active participant in building a technologically aware and active community of youngsters, thereby empowering them to solve the vital challenges of society through technology and alternative education. 
\end{itemize}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Government Engineering College}{Barton Hill, Thiruvananthapuram, India}
      {Bachelor of Technology in Electronics and Communication;  GPA: 6.72}{July. 2010 -- June. 2014}
    \resumeSubheading
      {Saraswathi Vidyalaya}{Vattiyoorkavu, Thiruvanathapuram, India}
      {CBSE  Percentage: 89}{June. 2008 -- March. 2010}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Triassic Solutions Pvt Ltd}{Technopark, Thiruvanathapuram, India}
      {Senior Software Engineer}{Jan 2016 - Present}
      \resumeItemListStart
        \resumeItem{APNHealth}
          {Worked for a new medical device company that has developed proprietary and patented software algorithms to create an innovative and cost-effective 3D cardiac imaging system. These algorithms are capable of using real-time 2D fluoroscopic image data to locate the precise 3D x-y-z location of cardiac catheters. This information is then incorporated with other integrated algorithms and a display screen to create 3D maps that can be used for catheter mapping and ablation of cardiac arrhythmia.Worked with industry leaders in implementing real-time systems for }
          \begin{itemize}
              \item Detecting catheters and other objects in fluoroscopic images.
              \item Cryoballoon localization.
              \item Developed 3D reconstruction technique for cardiac chamber locations.
              \item Respiration gating using back-projection of sequentially-acquired 2D fluoroscopy sequences, patient/table motion correction.
              \item Designed methodologies to foster the creation of novel software applications (patents pending).
         \end{itemize}
      \resumeItemListEnd

    \resumeSubheading
      {Triassic Solutions Pvt Ltd}{Technopark, Thiruvanathapuram, India}
      {Software Engineer}{July 2014 - Dec 2016}
      \resumeItemListStart
        \resumeItem{Aventri}
          {Build a very robust event management platform, custom tailored to clients' needs. As an architect, I drive the software architecture and platform choices made in my department. I manage external maintenance crews and work directly with technical teams to ensure 100 percent uptime for all our systems.
          \newline
          Build and maintained the company's first data warehousing system for reporting. This highly scalable platform includes a near real-time ETL process, allowing transactional data to be analyzed immediately. I'm also responsible for building the highly scalable 3 Stage (Dev, UAT, Prod) deployment pipeline and the fully automated alerting system supporting approximately 300 servers across 5 timezones.}
          \begin{itemize}
              \item Setup replicable Puppet based server deployment system in lines with the infrastructure should be code ideology.
              \item Setup a 3 Stage deployment system using Jenkins and Capistrano.
              \item Developed custom build and monitoring tools to support our multi-language codebases.
              \item Setup multi-stage alert systems using Nagios, Cloudwatch, and VictorOps to monitor and ensure uptime for our servers and other infrastructure.
              \item Setup advanced monitoring system to identify performance bottlenecks and codebase issues in various stages of development using New Relic and custom build debugger /audit tools.
         \end{itemize}
      \resumeItemListEnd
      
      \resumeSubheading
      {Communique}{Statue, Thiruvanathapuram, India}
      {Creative Consultant}{Jan 2013 - June 2014}
      \resumeItemListStart
        \resumeItem{Designer}
          {The Creative Internship at Communique gave me a thorough understanding as to how a branding agency works. Here I was responsible for creating design templates and fine-tuning designs to suit specific client needs. I was involved in making creatives, websites, documents and managing creative elements of the campaign.}
          \begin{itemize}
              \item Developed websites and worked in the branding campaign for Leela Backwaters.
              \item Designed creatives for the ADAM course for Mercedes - Benz.
              \item Worked on multiple magazines and creatives for different graduate schools.
         \end{itemize}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

      \resumeSubheading
      {Dionz}{Papanamcode, Thiruvanathapuram, India}
      {Lead Programmer}{Sept 2011 - Dec 2012}
      \resumeItemListStart
        \resumeItem{EEG Controlled Wheelchair}
          {Dionz stemmed from the idea of creating a "Mind Controlled Wheelchair" using EEG, as a consumer product, right after winning the title of "Manorama Yuva Mastermind".}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Volunteer Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sahridhaya}{Statue, Thiruvanathapuram, India}
      {Project Lead}{Jan 2015 - Present}
      \resumeItemListStart
      \newline
      Sahridhaya aims to bring the youth a fresh opportunity to participate in social events and establish the need for social responsibility and social commitment. Here I was responsible for designing and managing projects focusing on technical education among school and college students. As a part of the initiative, I lead the team that designed two projects.
        \resumeItem{Bit Please}
          {A 3-month long program college students to improve their coding skills and learn real-world engineering skills like software engineering, ML, data analysis, etc. The team has done fellowships with IIT-B in different areas. The current team is working with the district collectors office on optimization problems on different aspects of the city.}
        \resumeItem{Creating Unique Brains (CUB)}
          {A 3-month long program that identifies school students from socially weak backgrounds, providing technical skills to the team by partnering with interested college students and engaging the team in a socially relevant project.}

      \resumeItemListEnd

% %-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
